Greenhouse gas emissions model

### 2021-07-13 210617_GHG_model.Rmd
update references

The formulas come from Chapter 10 of the 2006 IPCC Guidelines for National Greenhouse Gas Inventories [@dong_ipcc_2006]. The document can be found on [the IPCC website](https://www.ipcc-nggip.iges.or.jp/public/2006gl/pdf/4_Volume4/V4_10_Ch10_Livestock.pdf).  Many variables are based on the work done in 'Variation in the carbon footprint of milk production on smallholder dairy farms in central Kenya' [@wilkes_variation_2020] and in 'Methods and guidance to support MRV of livestock emissions' [@wilkes_methods_2019].

*Here are our changes and additions to the original model:*

@@

library(decisionSupport)
###CW Note ####
# remove all the 'C:/Users/jwafula/Dropbox/UNIQUE_CCAFS/analysis/data/' business
###CW Note ####
### # This project will be stored in relative file paths (i.e. same or lower folders)
input_table <- "data/livestock_ghg_input_table.csv"
```

```{r make_variables}
# Generate a function for testing the model function 'line by line' 
# by taking a single random sample of the provided estimates
make_variables <- function(est,n=1){ x <- random(rho=est, n=n)
for(i in colnames(x)) assign(i, as.numeric(x[1,i]),envir=.GlobalEnv)}

>>>>

The formulas come from Chapter 10 of the *2006 IPCC Guidelines for National Greenhouse Gas Inventories* [@dong_ipcc_2006]. The document can be found on [the IPCC website](https://www.ipcc-nggip.iges.or.jp/public/2006gl/pdf/4_Volume4/V4_10_Ch10_Livestock.pdf). The chapter is part of the book *Good Practice Guidance and Uncertainty Management in National Greenhouse Gas Inventories* [@ipcc_good_2021] , also on the [the IPCC website](https://www.ipcc-nggip.iges.or.jp/public/gp/english/). Many variables are based on the work done in *Variation in the carbon footprint of milk production on smallholder dairy farms in central Kenya* [@wilkes_variation_2020] and in *Methods and guidance to support MRV of livestock emissions* [@wilkes_methods_2019].

**Here are our changes and additions to the original model:**

@@

library(decisionSupport)
###CW Note ####
# #### remove all the 'C:/Users/jwafula/Dropbox/UNIQUE_CCAFS/analysis/data/' folder locations throughout - 
#### these are not useful with RMD and RStudio / Git integrations
###CW Note ####
### # This project will be stored in relative file paths (i.e. same or lower folders)
input_table <- "data/livestock_ghg_input_table.csv"
```

Here we generate a `make_variables` function for testing the model function 'line by line'. We use it to take a single random sample of the provided estimates.

```{r make_variables}
###CW Note ####
### We will need to clean up the warnings later
### Reasonable ranges still missing for many variables
make_variables <- function(est,n=1){ x <- random(rho=est, n=n)
for(i in colnames(x)) assign(i, as.numeric(x[1,i]),envir=.GlobalEnv)}
